\begin{abstract}

The 13 years of the Cassini mission provide a unique dataset monitoring
the evolution of Titan’s atmosphere during almost half of Titan's year,
between the middle of the northern winter up to the northern summer solstice.
In this work we present a survey of the haze vertical extinction profiles retrieved
between 300 to 700 km altitude with an atmospheric limb multiple scattering model.
We analyze 138 ISS/NAC CL1-UV3 images taken between 2004 to 2017 covering the
entire Cassini mission.
We mainly focus on the temporal evolution of the haze content
in the upper atmosphere to track the evolution of the detached haze layer (DHL).
As previously reported by West et al. 2011 (GRL vol.38, L06204),
during the northern winter the DHL is present
at all latitudes below \ang{55}N and globally sunk to lower altitude
most rapidly at the vernal equinox in 2009.
No permanent DHL was observed in the UV3 filter between 2012 and 2015 but
we show that at the end of 2015, a new structure emerged from
the summer hemisphere (North) and propagated to the equator. This new layer
was not as pronounced and was much more complex than the one observed at the
beginning of the mission and was likely to be the initiation of a new DHL.
\change{When available, we }investigate the short time scale variability of the DHL
and no major changes is observed. Finally, we report some cases
where the viewing geometry allows us to probe the longitudinal variability
of the haze, highlighting some local inhomogeneities.
We notice that the extinction in the DHL is slightly higher in the dawn
side compare to the dusk side.
All these observations bring new perspectives
on the seasonal cycle of Titan's upper atmosphere, the evolution of the
DHL and its interaction with the dynamics.
The main seasonal pattern predicted by the global circulation models is consistent
with our findings, but the details and the timing of the global collapse
is not yet explained. Finally, comparisons with the UVIS instrument shows
that the haze extinction profiles retrieved during two stellar occultations
in 2009 are consistent with our results.

\end{abstract}

\keywords{Cassini --- Titan --- Haze --- Seasonal cycle}
