\section{Seasonal cycle of the haze extinction}

In order to provide a detailed explanation of the complex latitudinal variability of the detached haze layer, we present
some of the key images that we have analyzed. Based on our previous work, focused on the evolution of the detached haze in the
equatorial region \citep{West2018}, we define four different seasonal phase characteristics of the evolution of the detached haze layer.
Between 2004 and 2008, the DHL was stable in altitude and extinction profile.
Between 2008 and 2012, it settled and disappeared in the main haze below the 300 km.
During the period 2012-2016, the DHL was not observed and only sporadic transitory layers showed up in the UV3 images.
After 2016 and up to the end of the Cassini mission, the DHL reappeared following a complex pattern.
Here we illustrate the complete time and latitude survey, covering a period of time which includes about half a Titan year.
This is valuable because it encompasses the equinoctial transition period of 2009.
For each phase, we display the altitude and latitude distribution of the instantaneous haze extinction coefficient retrieved from intensities at the illuminated limb of Titan.
The same color scale is applied to all the panels in order to keep a consistent view on the whole data-set.
It corresponds to the range where the model have the best sensitivity at the UV wavelengths. In some cases, smaller features might be harder to highlight with this color scheme, however, all the results from theses panels are available to the reader for more in depth considerations (see Data Availablity section).
Locations where no data are available are left as blank areas on the panels.

\input{3.1-2004_2008.tex}
\input{3.2-2008_2012.tex}
\input{3.3-2012_2015.tex}
\input{3.4-2015_2017.tex}
